\vspace{-0.5cm}The X-shooter GTO sample of GRB afterglow and host Galaxy spectra

### 2016-12-02 document/XSGRB_sample.tex

\documentclass[iop, twocolappendix, numberedappendix, tighten, appendixfloats]{emulateapj}
\citestyle{apj}

\usepackage[stable]{footmisc}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{txfonts}
%\usepackage{hyperref}
\usepackage{natbib}
\bibpunct[, ]{(}{)}{;}{a}{}{,}
%\bibliographystyle{./bibtex/apj}

@@

\title{\vspace{-0.5cm}The X-shooter GTO sample of GRB afterglow and host Galaxy spectra}
\altaffiltext{$^{\dag}$}{Based on observations collected at the European Southern Observatory, Paranal, 
	Chile, Program ID: 084.A-0260, 085.A-009, 086.A-0073, 087.A-0055.}

\author{
	J.~Selsing\altaffilmark{1}, 
	D.~Malesani\altaffilmark{1}, 
	T.~Kr\"{u}hler\altaffilmark{1}, 
	P.~Goldoni\altaffilmark{14}, 
	J.~P.~U. Fynbo\altaffilmark{1}, 
	A.~de~Ugarte~Postigo\altaffilmark{11}, 
	J.~Japelj\altaffilmark{20},
	P.~D'Avanzo,
	Z.~Cano,
	S.~Covino\altaffilmark{10}, 
	V.~D'Elia\altaffilmark{7, 12}, 
	H.~Flores,
	O.~E.~Hartoog\altaffilmark{6},
	J.~Hjorth\altaffilmark{1}, 
	P.~Jakobsson\altaffilmark{5}, 
	A.~Levan,
	A.~Melandri,
	S.~Piranomonte \altaffilmark{7},
	R.~S\'anchez-Ram\'irez\altaffilmark{11},
	S.~Schulze\altaffilmark{17, 18}, 
	N.~R.~Tanvir\altaffilmark{19},
	C.~Th{\"o}ne,
	S.~D.~Vergani\altaffilmark{7, 8},
	P.~M.~Vreeswijk\altaffilmark{3}, 
	D.~J.~Watson\altaffilmark{1},
	K.~Wiersema\altaffilmark{19},
	D.~Xu\altaffilmark{1}
	L.~Christensen\altaffilmark{1},
	A.~De~Cia\altaffilmark{3}, 
	L.~Kaper\altaffilmark{6}, 
	L.~A.~Antonelli,
	F.~Fiore,
	A.~Gomboc,
	P.~Groot,
	F.~Hammer,
	C.~Ledoux\altaffilmark{2}, 
	E.~Maiorano,
	B.~Milvang-Jensen\altaffilmark{1}, 
	E.~Palazzi,
	E.~Pian,
	J.~Schaye,
	G.~Tagliaferri\altaffilmark{7},
	R.~A.~M.~J.~Wijers\altaffilmark{6}
}

\altaffiltext{1}{Dark Cosmology Centre, Niels Bohr Institute, University of Copenhagen, Juliane Maries Vej 30, 2100 K\o benhavn \O, Denmark}
\altaffiltext{2}{European Southern Observatory, Alonso de C\'{o}rdova 3107, Vitacura, Casilla 19001, Santiago 19, Chile}
\altaffiltext{3}{Department of Particle Physics and Astrophysics, Faculty of Physics, Weizmann Institute of Science, Rehovot 76100, Israel}
\altaffiltext{4}{Th\"uringer Landessternwarte Tautenburg, Sternwarte 5, 07778 Tautenburg, Germany}
\altaffiltext{5}{Centre for Astrophysics and Cosmology, Science Institute, University of Iceland, Dunhagi 5, IS-107 Reykjavik, Iceland}
\altaffiltext{6}{Astronomical Institute Anton Pannekoek, University of Amsterdam, Science Park 904, NL-1098 XH Amsterdam, the Netherlands}
\altaffiltext{7}{INAF-Osservatorio Astronomico di Roma, Via Frascati 33, I-00040 Monteporzio Catone, Italy}
\altaffiltext{8}{GEPI-Observatoire de Paris, CNRS UMR 8111, Univ. Paris-Diderot, 5 Place Jules Janssen - 92190 Meudon, France}
\altaffiltext{9}{American River College, Physics and Astronomy Dpt., 4700 College Oak Drive, Sacramento, CA 95841, USA}
\altaffiltext{10}{INAF, Osservatorio Astronomico di Brera, Via E. Bianchi 46, I-23807 Merate, Italy}
\altaffiltext{11}{Instituto de Astrof\'{\i}sica de Andaluc\'{\i}a (IAA-CSIC), Glorieta de la Astronom\'{\i}a s/n, 18008, Granada, Spain}
\altaffiltext{12}{ASI-Science Data Centre, Via Galileo Galilei, I-00044 Frascati, Italy}
\altaffiltext{13}{Institute of Experimental and Applied Physics, Czech Technical University in Prague, Horska 3a/22, 128 00 Prague 2, Czech Republic}
\altaffiltext{14}{APC, Astroparticules et Cosmologie, Universite Paris Diderot, CNRS/
	IN2P3, CEA/Irfu, Observatoire de Paris, Sorbonne Paris Cite, 10, Rue Alice Domon et L
	eonie Duquet, 75205 Paris Cedex 13, France}
\altaffiltext{15}{Max-Planck-Institut f\"{u}r extraterrestrische Physik, Giessenbachs
	tra\ss e, 85748 Garching, Germany}
\altaffiltext{16}{Universit\`a degli studi di Milano-Bicocca, Piazza della Scienza 3,
	20126, Milano, Italy}
\altaffiltext{17}{Pontificia Universidad Cat\'{o}lica de Chile, Departamento de Astro
	nom\'{\i}a y Astrof\'{\i}sica, Casilla 306, Santiago 22, Chile}
\altaffiltext{18}{Millennium Center for Supernova Science}
\altaffiltext{19}{Department of Physics and Astronomy, University ofLeicester, University Road, Leicester, LE1 7RH, UK}
\altaffiltext{20}{University of Ljubljana,Department of Physics,Faculty of Mathematics \& Physics,SI}\

\begin{abstract}
The {\it Swift} satellite allows us to use gamma-ray bursts (GRBs) to peer into 
the hearts of star forming galaxies through cosmic time. Our open
collaboration, representing most of the active ESO member researchers in this
field, seeks to build a public legacy sample of GRB X-shooter spectroscopy
while {\it Swift} continues to fly. We propose to continue our programme to target
all suitably observable GRB afterglows (up to 15 bursts per semester), with the
primary goal of producing a well-defined, homogeneous, statistically useful
sample. To date, our spectroscopy covers a redshift range from 0.059 to about
8, with more than 20 robust metallicity measurements from absorption lines (over 
the redshift range 1.7--5.9) and 4 secure detections of H$_2$ or CH molecular
absorption. Such information is extremely difficult to obtain by other means.
In terms of studying the spread and redshift evolution in gas-phase properties, the
sample is still limited by low-number statistics. 
\end{abstract}

@@

@@

\begin{enumerate}
	\item GRB triggered onboard by Swift.
	\item Galactic $A_V \lesssim 0.5$ mag.
	\item XRT started observing within 10 minutes since the GRB; an XRT position must be distributed within 12 hr.
	\item The target must be visible for at least 60 min at least 30° above horizon, with the Sun below -12°.
	\item No bright closeby stars.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Observations}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

The remaining offset is corrected by cross-correlation with a synthetic sky
spectrum \citep{Noll2012, Jones2013}. To get the correct seeing PSF with which
to convolve the synthetic sky an initial refinement of the wavelength solution
have been obtained by cross-correlating the observed sky with an unconvolved
synthetic sky. This preliminary wavelength calibration is applied to the
observed sky. The synthetic spectrum is then convolved with an increasing seeing
PSF and the width that minimizes $\chi^2$ with the updated observed sky is
chosen to be the effective sky-PSF. Using the synthetic sky with the matched
resolution, a final wavelength calibration can then be calculated by
cross-correlating the observed sky with the correctly broadened sky spectrum, as
a function of a velocity offset. Both a multiplicative and an additive offset to
the wavelength calibration has been tested, but in terms of $\chi^2$, the model
with only a multiplicative offset is preferred.

@@

@@

In cases where multiple traces are visible in the slit, additional components
for the profile are used in the optimal extraction. The additional components
share the PSF parameters and in cases where the additional component is an
extended object, the fits have been inspected to ensure that the additional
component does now skew the fit towards a broader PSF. The additional
components are not used for the weights.

@@

\input{tables/burst_overview.tex}

@@

\def\aj{AJ}
\def\araa{ARA\&A}
\def\apj{ApJ}
\def\apjl{ApJL}
\def\apjs{ApJS}
\def\apss{Ap\&SS}
\def\aap{A\&A}
\def\aapr{A\&A~Rev.}
\def\aaps{A\&AS}
\def\mnras{MNRAS}
\def\nat{Nature}
\def\pasp{PASP}
\def\aplett{Astrophys.~Lett.}

\bibliographystyle{apj}
\bibliography{XSGRB_sample}
%\bibliography{thebib}

@@

>>>>

%                                                                 aa.dem
% AA vers. 8.2, LaTeX class for Astronomy & Astrophysics
% demonstration file
%                                                       (c) EDP Sciences
%-----------------------------------------------------------------------
%
%\documentclass[referee]{aa} % for a referee version
%\documentclass[onecolumn]{aa} % for a paper on 1 column  
%\documentclass[longauth]{aa} % for the long lists of affiliations 
%\documentclass[rnote]{aa} % for the research notes
%\documentclass[letter]{aa} % for the letters 
%\documentclass[bibyear]{aa} % if the references are not structured 
% according to the author-year natbib style

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass{aa}    %% Astronomy & Astrophysics style class aa.cls v8.2
%\documentclass[referee]{aa}

\usepackage{graphicx,url,twoopt,natbib}
\usepackage[varg]{txfonts}           %% A&A font choice

\usepackage{pdfcomment}              %% for popup acronym meanings
\usepackage{acronym}                 %% for popup acronym meanings

\usepackage{url}
\usepackage{color,hyperref}
\definecolor{linkcolor}{rgb}{0,0,0.7}
\hypersetup{colorlinks=true,
	linkcolor=linkcolor, 
	citecolor=linkcolor,
	filecolor=linkcolor, 
	urlcolor=linkcolor}

\usepackage{natbib}

\bibliographystyle{aa}
\bibpunct{(}{)}{;}{a}{}{,}    %% natbib cite format used by A&A and ApJ

@@

\title{\vspace{-0.5cm}The X-shooter GTO sample of GRB afterglow and host Galaxy spectra}
\thanks{Based on observations collected at the European Southern Observatory, Paranal, 
	Chile, Program ID: 098.A-0055, 097.A-0036, 096.A-0079, 095.B-0811(B), 
	095.A-0045, 094.A-0134, 093.A-0069, 092.A-0124, 0091.C-0934, 090.A-0088,
	089.A-0067, 088.A-0051, 087.A-0055, 086.A-0073, 085.A-0009 and 084.A-0260}

\titlerunning{XSGRB sample}

\author{
	J.~Selsing\inst{1}, 
	D.~Malesani\inst{1}, 
	T.~Kr\"{u}hler\inst{1}, 
	P.~Goldoni\inst{14}, 
	J.~P.~U. Fynbo\inst{1}, 
	A.~de~Ugarte~Postigo\inst{11}, 
	J.~Japelj\inst{20},
	P.~D'Avanzo,
	Z.~Cano,
	S.~Covino\inst{10}, 
	V.~D'Elia\inst{7, 12}, 
	H.~Flores,
	O.~E.~Hartoog\inst{6},
	J.~Hjorth\inst{1}, 
	P.~Jakobsson\inst{5}, 
	A.~Levan,
	A.~Melandri,
	S.~Piranomonte \inst{7},
	R.~S\'anchez-Ram\'irez\inst{11},
	S.~Schulze\inst{17, 18}, 
	N.~R.~Tanvir\inst{19},
	C.~Th{\"o}ne,
	S.~D.~Vergani\inst{7, 8},
	P.~M.~Vreeswijk\inst{3}, 
	D.~J.~Watson\inst{1},
	K.~Wiersema\inst{19},
	D.~Xu\inst{1}
	L.~Christensen\inst{1},
	A.~De~Cia\inst{3}, 
	L.~Kaper\inst{6}, 
	L.~A.~Antonelli,
	F.~Fiore,
	A.~Gomboc,
	P.~Groot,
	F.~Hammer,
	C.~Ledoux\inst{2}, 
	E.~Maiorano,
	B.~Milvang-Jensen\inst{1}, 
	E.~Palazzi,
	E.~Pian,
	J.~Schaye,
	G.~Tagliaferri\inst{7},
	R.~A.~M.~J.~Wijers\inst{6}
}

\authorrunning{Selsing et al.}

\institute{Dark Cosmology Centre, Niels Bohr Institute, University of Copenhagen, Juliane Maries Vej 30, 2100 K\o benhavn \O, Denmark
\and European Southern Observatory, Alonso de C\'{o}rdova 3107, Vitacura, Casilla 19001, Santiago 19, Chile
\and Department of Particle Physics and Astrophysics, Faculty of Physics, Weizmann Institute of Science, Rehovot 76100, Israel
\and Th\"uringer Landessternwarte Tautenburg, Sternwarte 5, 07778 Tautenburg, Germany
\and Centre for Astrophysics and Cosmology, Science Institute, University of Iceland, Dunhagi 5, IS-107 Reykjavik, Iceland
\and Astronomical Institute Anton Pannekoek, University of Amsterdam, Science Park 904, NL-1098 XH Amsterdam, the Netherlands
\and INAF-Osservatorio Astronomico di Roma, Via Frascati 33, I-00040 Monteporzio Catone, Italy
\and GEPI-Observatoire de Paris, CNRS UMR 8111, Univ. Paris-Diderot, 5 Place Jules Janssen - 92190 Meudon, France
\and American River College, Physics and Astronomy Dpt., 4700 College Oak Drive, Sacramento, CA 95841, USA
\and INAF, Osservatorio Astronomico di Brera, Via E. Bianchi 46, I-23807 Merate, Italy
\and Instituto de Astrof\'{\i}sica de Andaluc\'{\i}a (IAA-CSIC), Glorieta de la Astronom\'{\i}a s/n, 18008, Granada, Spain
\and ASI-Science Data Centre, Via Galileo Galilei, I-00044 Frascati, Italy
\and Institute of Experimental and Applied Physics, Czech Technical University in Prague, Horska 3a/22, 128 00 Prague 2, Czech Republic
\and APC, Astroparticules et Cosmologie, Universite Paris Diderot, CNRS/
	IN2P3, CEA/Irfu, Observatoire de Paris, Sorbonne Paris Cite, 10, Rue Alice Domon et L
	eonie Duquet, 75205 Paris Cedex 13, France
\and Max-Planck-Institut f\"{u}r extraterrestrische Physik, Giessenbachs
	tra\ss e, 85748 Garching, Germany
\and Universit\`a degli studi di Milano-Bicocca, Piazza della Scienza 3,
	20126, Milano, Italy
\and Pontificia Universidad Cat\'{o}lica de Chile, Departamento de Astro
	nom\'{\i}a y Astrof\'{\i}sica, Casilla 306, Santiago 22, Chile
\and Millennium Center for Supernova Science
\and Department of Physics and Astronomy, University ofLeicester, University Road, Leicester, LE1 7RH, UK
\and University of Ljubljana,Department of Physics,Faculty of Mathematics \& Physics,SI}

\date{Received/ accepted}

\abstract{
The {\it Swift} satellite allows us to use gamma-ray bursts (GRBs) to peer into 
the hearts of star forming galaxies through cosmic time. Our open
collaboration, representing most of the active ESO member researchers in this
field, seeks to build a public legacy sample of GRB X-shooter spectroscopy
while {\it Swift} continues to fly. We propose to continue our programme to target
all suitably observable GRB afterglows (up to 15 bursts per semester), with the
primary goal of producing a well-defined, homogeneous, statistically useful
sample. To date, our spectroscopy covers a redshift range from 0.059 to about
8, with more than 20 robust metallicity measurements from absorption lines (over 
the redshift range 1.7--5.9) and 4 secure detections of H$_2$ or CH molecular
absorption. Such information is extremely difficult to obtain by other means.
In terms of studying the spread and redshift evolution in gas-phase properties, the
sample is still limited by low-number statistics. 
}

@@

\maketitle

@@

\begin{enumerate}
	\item GRB triggered onboard by Swift.
	\item Galactic $A_V \lesssim 0.5$ mag.
	\item XRT started observing within 10 minutes since the GRB; an XRT position must be distributed within 12 hr.
	\item The target must be visible for at least 60 minutes at least 30 degrees above the horizon, with the Sun below -12.
	\item No bright closeby stars.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Observations} \label{obs}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

The remaining offset is corrected by cross-correlation with a synthetic sky
spectrum \citep{Noll2012, Jones2013} after the continuum, estimated as the mode
of all flux values, has been subtrated. To get the correct seeing PSF with which
to convolve the synthetic sky an initial refinement of the wavelength solution
have been obtained by cross-correlating the observed sky with an unconvolved
synthetic sky. This preliminary wavelength calibration is applied to the
observed sky. The synthetic spectrum is then convolved with an increasing seeing
PSF and the width that minimizes $\chi^2$ with the updated observed sky is
chosen to be the effective sky-PSF. Using the synthetic sky with the matched
resolution, a final wavelength calibration can then be calculated by
cross-correlating the observed sky with the correctly broadened sky spectrum, as
a function of a velocity offset. Both a multiplicative and an additive offset to
the wavelength calibration has been tested, but in terms of $\chi^2$, the model
with only a multiplicative offset is preferred.

@@

Using the convolved synthetic sky, the $\gtrsim 3 \sigma$ sky brightness pixels
have been added to the bad pixel map to avoid the cores of the brightest
sky-lines.

@@

To extract the afterglow spectrum from the rectified 2D-image, several
techniques have been employed based on the brightness of the afterglow and the
complexity of the objects entering the slit. Due to the malfunctioning ADC, see
Sect. \ref{obs}, the spectral trace moves across the slit as a function of
wavelength for a large fraction of the bursts observed meaning that using a
single aperture for the spectral extraction is inadequate due to the large
amount of background that would then enter the slit. To optimally select the
extraction regions we therefore need to model the trace position.

To get the shape and the position of the spectral PSF as a function of location
on the image, we need to chose a model which can represent how the light falls
on the slit. We know from \citet{Trujillo2001} that the Moffat function
\citep{Moffat1969} adequately describes an imaging PSF due to atmospheric
turbulence, but due to the aberrations in the dispersion elements and the
rectification process, the PSF we are trying to model different from this
profile. To allow for flexibility in the model, we have chosen the Voigt
function as a model for the spectral PSF and we describe how this is evaluated
in App. \ref{voigt}. Since additionally, the host galaxy could also have a
contribution the image profile, this choice allows for the required freedom if
additional flux is in the wings of the profile.

To guide the guess position of the trace on the slit as a function of
wavelength, we have used the analytic prescription for the trace position
described in \citet{Filippenko1982}, where the header keywords of the
observations have been queried for the ambient conditions which controls the
degree to which the trace moves.

Based on the signal-to-noise of the afterglow continuum, the 2D-image has been
binned down in the spectral direction to a number of elements that allows for an
accurate tracing of the PSF, typically 200 bins for moderate signal-to-noise.
For each of the bins and using the guess position, the spectral PSF has been fit
using the unweighted chi-squared minimization algorithm implemented in
\texttt{scipy.optimize.curve\_fit} \citep{scipy}. Since we know that the trace
varies slowly as a function of wavelength, we have then fitted a low-order
polynomial to the fit parameters as a function of wavelength, which allows us to
evaluate the spectral PSF at all wavelengths and this way accurately model the
entire spectral PSF.

Equipped with a model for how the light falls on the entire image, we can then
employ the optimal extraction algorithm \cite{Horne1986}, which weights the
extraction aperture by the spectral profile, or alternatively sum all pixels
within 1 FWHM of the modeled profile. Where possible, we have used the optimal
extraction. In cases where the trace is very weak, even in the binned images, an
aperture has been selected manually which covers emission lines, if present, and
when nothing is immediately visible, the entire nodding window. The error- and
bad pixel maps are in all cases propagated throughout the extraction.

In cases where multiple traces are visible in the slit, additional components
for the profile are used in the optimal extraction. The additional components
do not share the PSF parameters and in cases where the additional component is an
extended object, the fits have been inspected to ensure that the additional
component does now skew the fit towards a different PSF. The additional
components are not used for the weights.

The spectra are corrected for galactic extinction using the E(B-V) value from
the dust maps of \citet{Schlegel1998} with the update in
\citet{Schlafly2011}\footnote{Queried from
	http://irsa.ipac.caltech.edu/applications/DUST/index.html using
	\citet{astroquery}}, and the extinction curve by \cite{Cardelli1989} with a
total to selective extinction $R_V = 3.1$. The wavelengths of the extracted
1D-spectra are moved to vacuum, moved to the barycentric frame, and the
wavelength recalibration described in Sect. \ref{wavecal} is applied. Pixels
with pixel-to-pixel variation large than $50 \sigma$ are added to the bad pixel
map.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Telluric correction} \label{tell_corr}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

For all earth-based telescopes the light of interest has to pass through Earths
atmosphere, where the atmospheric content and conditions make an imprint on the
received spectrum. These telluric features can be calculated in a multitude of
ways and we employ a prioritized list of methods here, depending on the
availability of the different method. Since the observation are often taken at
odd times under varying conditions, this prioritized list ensures that we are
always doing the optimal correction.

The highest priority method is using the GRB afterglow continuum itself, where
the atmospheric conditions have directly been imprinted on the spectrum. The
telluric features can directly be fit with an atmospheric model
\citep{Smette2015, Kausch2015}, which can then be to correct for the absorption.
The requirement here is that the afterglow continuum spectrum has a
signal-to-noise higher than a value of 10.

If the afterglow is not sufficiently bright, telluric standard stars observed
close in the time to the GRB can be used as a proxy for the atmospheric
condition during the GRB observation. Here we employ the telluric correction
method that has been developed in \citet{Selsing2015}, where a library of
synthetic templates is fit to the observed telluric standard.

In the last case, where the object is neither bright enough, or there for some
reason have not been observed a telluric standard, we rely on the synthetic sky
model by \citep{Noll2012, Jones2013} for which we generate a synthetic
transmission spectrum, which we then use, where the ambient parameters for the
observations have been used.

@@

%\input{tables/burst_overview.tex}

@@

\bibliography{XSGRB_sample}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{The complex error function and the Voigt profile} \label{voigt}
When modeling the spectral PSF, we need to evaluate the Voigt-profile. The Voigt profile, which is the convolution of the Gaussian and Lorentzian profiles, can, centered at zero, be written as \citep{pagnini2010} 
\begin{equation} 
\begin{split}
V(\lambda,\sigma, \gamma)  
& = G(\lambda, \sigma)  \otimes L(\lambda, \gamma) \\
& = \int_{-\infty}^{\infty} G(\xi, \sigma) L(\lambda - \xi, \gamma) d\xi \\
& = \int_{-\infty}^{\infty} \frac{1}{\sqrt{2 \pi} \sigma} e^{- \left( \frac{\xi}{\sqrt{2} \sigma}  \right)^2 } \frac{1}{\gamma \pi} \frac{\gamma^2}{(\lambda - \xi)^2 + \gamma^2} d\xi \\
& = \frac{\gamma}{\sqrt{2} \sigma} \frac{1}{ \pi^{3/2}}   \int_{-\infty}^{\infty} \frac{e^{- \left( \frac{\xi}{\sqrt{2} \sigma}  \right)^2 }}{(\lambda - \xi)^2 + \gamma^2}.
\end{split}
\end{equation}
We can by making the following substitution, $\xi = \sqrt{2} \sigma$ and $d\xi = \sqrt{2} \sigma dt$, write it as
\begin{equation} 
\begin{split}
V(\lambda,\sigma, \gamma)  
& =  \frac{\sqrt{2} \sigma}{ \sqrt{{\pi}}} \frac{\frac{\gamma}{\sqrt{2} \sigma}}{\pi}  \int_{-\infty}^{\infty} \frac{e^{- t^2 }}{(\lambda - \sqrt{2} \sigma t)^2 + \gamma^2} dt \\
& = \frac{1}{\sqrt{2 \pi} \sigma}  \frac{\frac{\gamma}{\sqrt{2} \sigma}}{\pi}  \int_{-\infty}^{\infty} \frac{e^{- t^2 }}{\left(\frac{\lambda}{\sqrt{2} \sigma} -  t\right)^2 + \left(\frac{\gamma}{\sqrt{2} \sigma}\right)^2} dt.	
\end{split}
\end{equation}
This form of the convolution is closely related to the complex probability function \citep{letchworth2007, abrarov2015a},
\begin{equation} 
\begin{split}
W(z)  
& = \frac{i}{\pi} \int_{-\infty}^{\infty} \frac{e^{-t^2}}{z - t}  
\end{split}
\end{equation}
for any complex argument, $z = x + iy$. The complex probability function can be expressed as a sum of a real an imaginary part \citep{benner1995, abrarov2015b},
\begin{equation} 
\begin{split}
W(x, y)  
& = K(x, y) + i L(x, y) \\
& = \frac{y}{\pi}  \int_{-\infty}^{\infty} \frac{e^{- t^2 }}{(x -  t)^2 +y^2} dt  + \frac{i}{\pi}  \int_{-\infty}^{\infty} \frac{(x - t)e^{- t^2 }}{(x -  t)^2 +y^2} dt,
\end{split}
\end{equation}
where is the real part, $\mathtt{Re}[W(x, y)] =  \sqrt{2 \pi} \sigma V(\lambda,\sigma, \gamma)$ if $x = \frac{\lambda}{\sqrt{2} \sigma}$ and $y = \frac{\gamma}{\sqrt{2} \sigma}$, which can be obtained by using the complex argument, $z = \frac{\lambda + i\gamma}{\sqrt{2} \sigma}$, in the complex probability function. If $\mathtt{Im}[z] \geq 0$, which is always guaranteed for the width of a spectral profile, the complex probability function equals the complex error function. The complex error function has numerous, fast, numerical approximations where in this work we use the \texttt{scipy.special.wofz} \citep{scipy} implementation.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
